The Key to a Data Parallel Compiler

### 2016-05-10 2016-spring-array/2016-array-key.tex
More fixes from Camera Ready Audit.
Copyright information

\toappear{}

\authorinfo{Aaron W. Hsu}{Indiana University}{awhsu@indiana.edu}

@@

We have demonstrated the technique and the core insights behind the
data structures involved. It presents a solution to a very old and
traditional problem in a very uncommon light, by eschewing the common
practices that underlie every other significant and general solution
found in modern compilers today and replacing them with an entirely
different paradigm centered on parallelism and aggregate operations.

\balancecolumns

>>>>

\toappear{Permission to make digital or hard copies of all or part of this
work for personal or classroom use is granted without fee provided that copies
are not made or distributed for profit or commercial advantage and that copies
bear this notice and the full citation on the first page. Copyrights for
components of this work owned by others than the author(s) must be honored.
Abstracting with credit is permitted. To copy otherwise, or republish, to post
on servers or to redistribute to lists, requires prior specific permission
and/or a fee. Request permissions from Permissions@acm.org.

\emph{ARRAY'16}, June 13-17 2016, Santa Barbara, CA, USA

Copyright is held by the owner/author(s). Publication rights licensed to ACM.

ACM 978-1-4503-4384-8/16/06…\$15.00

DOI: http://dx.doi.org/10.1145/2935323.2935331}

\authorinfo{Aaron W. Hsu}{Indiana University, USA}{awhsu@indiana.edu}

@@

We have demonstrated the technique and the core insights behind the
data structures involved. It presents a solution to a very old and
traditional problem in a very uncommon light, by eschewing the common
practices that underlie every other significant and general solution
found in modern compilers today and replacing them with an entirely
different paradigm centered on parallelism and aggregate operations.
\balancecolumns
